---
title: 'Developing Data Products Course Project: Shiny App'
author: "Akylai Mk"
date: "October 3, 2020"
output: 
        ioslides_presentation:
                transition: 0.5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
The mortality rate in Kyrgyz Republic depends on time period, region, reason for death:
- region: There are 7 regions in the country, and a capital Bishkek city
- year: Available data given for 1998-2019
- reason for death: different reasons are grouped into 18 major categories

This shiny app helps understand mortality in Kyrgyzstan through data.

## Documentation
Data was taken from the National Statistical Committee of Kyrgyz Republic, www.stat.kg


Output plots can be manipulated by choosing the reason for death and the region.

The materials can be found in GitHub Repo: https://github.com/Akylai-mk/developing-data-products-course-project
The shiny app is available at: https://akylaimk.shinyapps.io/mortalityKR/



## Code plots that shiny app will produce. Part 1

```{r, echo=TRUE, warning=FALSE, message=FALSE, results='hide', eval=FALSE}
library(shiny)
library(readxl)
library(ggplot2)
# Define UI for application that draws a histogram
shinyUI(fluidPage(
    # Application title
    titlePanel("Understanding mortality in Kyrgyz Republic through data"),
    # Sidebar with input for reason and line color
       sidebarLayout(    
    sidebarPanel(
            selectInput("reason", h3("Select reason for death"),
                        choices = c("infections", "Neoplasms",
                                       "blood", "Endocrine", 
                                       "Mental", "nervousSystem",
                                       "earMastoid", 
                                       "circulatorySystem",
                                       "Respiratory", "DigestiveSystem",
                                      
        
```

## Code plots that shiny app will produce. Part 2
```{r, echo=TRUE, warning=FALSE, message=FALSE, results='hide', eval=FALSE} 
 "skin", "musculoskeletalSystem",
                                       "GenitourinarySystem", "Pregnancy",
                                       "perinatal", "CongenitalChromosomal",
                                       "Abnormal", "InjuryPoisoning"),
                        selected = 1)),
        # Show a plot of the mortality
        mainPanel(
            h3("Mortality in Kyrgyz Republic over time"),
            plotOutput("mortalityPlot"))
        )
))
shinyServer(function(input, output) {
    ##Read my data
    myDF <- read_excel("mortality.xls")
       output$mortalityPlot <- renderPlot({
       
```

## Code plots that shiny app will produce. Part 3
```{r, echo=TRUE, warning=FALSE, message=FALSE, results='hide', eval=FALSE} 
dataReason <- switch(input$reason,
                      "infections" = myDF$infections,
                      "Neoplasms"=myDF$Neoplasms,
                      "blood"=myDF$blood, 
                      "Endocrine"=myDF$Endocrine, 
                      "Mental"=myDF$Mental, 
                      "nervousSystem"=myDF$nervousSystem,
                      "earMastoid"=myDF$earMastoid, 
                      "circulatorySystem"=myDF$circulatorySystem,
                      "Respiratory"=myDF$Respiratory, 
                      "DigestiveSystem"=myDF$DigestiveSystem,
                      "skin"=myDF$skin, 
                      "musculoskeletalSystem"=myDF$musculoskeletalSystem,
                      "GenitourinarySystem"=myDF$GenitourinarySystem, 
                      "Pregnancy"=myDF$Pregnancy,
                 
```

## Code plots that shiny app will produce. Part 4
```{r, echo=TRUE, warning=FALSE, message=FALSE, results='hide', eval=FALSE} 

                      "perinatal"=myDF$perinatal, 
                      "CongenitalChromosomal"=myDF$CongenitalChromosomal,
                      "Abnormal"=myDF$Abnormal, 
                      "InjuryPoisoning"=myDF$InjuryPoisoning)
              ggplot() +
        geom_line(myDF, mapping = aes(year, dataReason, color = region))
           })

})
```
## Links and references
- shiny app: https://akylaimk.shinyapps.io/mortalityKR/

- Link to github: https://github.com/Akylai-mk/developing-data-products-course-project

- data taken from http://stat.kg/en/statistics/zdravoohranenie/


## Thank you!
